%-------------------------
% Resume in Latex
% Author : Saumitra Kumar
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\href{http://sourabhbajaj.com/}{\Large Jyoti Dhyani}} & Email : \href{mailto:jdhyani@expediagroup.com}{jdhyani@expediagroup.com}\\
\href{https://www.linkedin.com/in/jyoti-dhyani-308511139/}{LinkedIn} & Mobile : \href{tel:+08826775441}{+91-8826775441} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Expedia Group}{Gurgaon}
{Software Development Engineer III}{Oct 2021 – Current}
\resumeItemListStart
\resumeItem{Integrated OneKey points for the Activities shopping path, leading to a 15\% increase in conversion rates and a 20\% boost in revenue.}
\resumeItem{Spearheaded the migration of Activities PDP components into shared-ui following the SDUI approach, resulting in a 20\% reduction in code duplication and a 30\% improvement in development time.}
\resumeItem{Developed and delivered cross-selling activities on Hotels PDP, contributing to a \$500k increase in quarterly revenue and a 10\% increase in customer engagement metrics.}
\resumeItem{Led a session in the EG India UI community sync on developing a new component in shared-ui for Activities SRP, facilitating knowledge sharing and collaboration across teams.}
\resumeItem{Created and maintained monitoring dashboards and alerts for the activities experience layer and PWA using Datadog, leading to a 20\% decrease in system downtime and a 15\% improvement in response time.}
\resumeItem{Introduced caching in GHA workflows, reducing build times by 30\% and improving developer productivity.}
\resumeItem{Integrated renovate to automate dependency updates, resulting in a 50\% reduction in manual maintenance efforts and a 20\% decrease in dependency-related issues.}
\resumeItemListEnd

\resumeSubheading
{InfoEdge}{Delhi}
{Senior Front End Engineer}{Nov 2019 – Oct 2021}
\resumeItemListStart
\resumeItem{Established a CI/CD pipeline in Github, automating code checks, testing, and deployment to facilitate a seamless development lifecycle.}
\resumeItem{Configured webpack and babel to generate optimized builds for modern and legacy browsers, resulting in a 25\% reduction in bundle size and a 20\% improvement in page load times on modern browsers.}
\resumeItem{Successfully delivered multiple frontend projects using ReactJS, Redux, and JavaScript, ensuring timely delivery and receiving positive feedback from stakeholders.}
\resumeItem{Conducted comprehensive unit testing of React components using jest and enzyme, achieving a 90\% test coverage rate and reducing production bugs by 30\%.}
\resumeItem{Implemented industry best practices for UI development, emphasizing reusable, mobile-first, and responsive design principles using Bootstrap and ReactJS, resulting in a 20\% increase in mobile traffic and a 15\% improvement in user engagement metrics.}
\resumeItem{Implemented data-driven A/B tests to evaluate the effectiveness of new product page designs and inform decision-making processes.}
\resumeItemListEnd


\resumeSubheading
{NIIT Technologies}{Delhi}
{Software Developer}{Aug 2017 – Nov 2019}
\resumeItemListStart
\resumeItem{Translated Figma designs into HTML, CSS, and JavaScript in collaboration with the product team and UX designers, enhancing the design and functionality of the product.}
\resumeItem{Migrated the site to a self-documenting, isolated, and testable JavaScript framework, simplifying development processes and facilitating collaboration among developers.}
\resumeItem{Developed UI with a focus on reusable, mobile-first, and responsive design principles using Bootstrap and ReactJS, resulting in improved user experience and engagement.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
%\resumeSubHeadingListStart
%\resumeSubItem{QuantSoftware Toolkit}
%{Open source python library for financial data analysis and machine learning for finance.}
%\resumeSubItem{Github Visualization}
%{Data Visualization of Git Log data using D3 to analyze project trends over time.}
%\resumeSubItem{Recommendation System}
%{Music and Movie recommender systems using collaborative filtering on public datasets.}
%\resumeSubItem{Mac Setup}
%{Book that gives step by step instructions on setting up developer environment on Mac OS.}
%\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\item{
\textbf{Frontend Technologies}{: React.js, Redux, JavaScript, GraphQL, HTML5, CSS3, SASS}
}
\item{
\textbf{Testing Frameworks}{: Cypress, Jest, Enzyme, Testing Library}
}
\item{
\textbf{Monitoring \& Logging}{: Splunk, Datadog, Apollo Studio}
}
\item{
\textbf{Cloud \& DevOps}{: Docker, Kubernetes, AWS}
}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Indira Gandhi Delhi Technical University}{Delhi, India}
{Bachelor of Technology, Information Technology;  GPA: 4.00}{Aug. 2013 -- June. 2017}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
