%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
%\fancyfoot[C]{\it{Find me at: \href{\src}{\src}}}
\cfoot{\makebox[\textwidth][c]{\it{Find me at: \href{\src}{\src}}}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\def\name{Marcell Douglas Nagy}
\def\email{marcelldnagy@gmail.com}
\def\mobile{+44 7425 858825}
%\def\mobile{+2779 999 5753}
\def\website{https://www.linkedin.com/in/marcell-nagy-83b8a1a9/}
\def\src{https://github.com/262882/resume}
\def\repo{https://github.com/marcelldls}
\def\nation{HUN, RSA, UK Settled}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{\website}{\Large \name}} & Email: \href{mailto:\email}{\email}\\
  \href{\website}{\website} & Mobile: \href{tel:\mobile}{\mobile} \\
  \href{\repo}{\repo} & Nationality: \nation \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Diamond Light Source}{Harwell Science Campus, UK}
      {Software Systems Engineer: Beamline Controls Core Development Team}{May 2023 - Present}
      \resumeItemListStart
        \resumeItem{Description}
          {The design, development, commissioning and operational support of software and distributed control systems to support the development and operations of the beamlines of the synchrotron}
        \resumeItem{Technologies}
          {Python, BASH, Linux, Git, Docker, Kubernetes}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {University Of The Witwatersrand}{Johannesburg, RSA}
      {Faculty Tutor: School of Computer Science and Applied mathematics}{Feb. 2022 - April 2023}
      \resumeItemListStart
        \resumeItem{Description}
          {Supporting teaching activities for various courses. Introduction to Algorithms and Programming, Introduction to Data Structures and Algorithms, Basic Computer Organisation, Advanced topics in Robotics.}
         \resumeItem{Technologies}
          {Python, C++, Linux, ROS, Arduino, Computer Vision}
      \resumeItemListEnd
      
    \resumeSubheading
      {Diamond Light Source}{Harwell Science Campus, UK}
      {Mechanical Design Engineer: Beamline Engineering Team}{Jan. 2019 - Feb. 2022}
      \resumeItemListStart
        \resumeItem{Description}
          {The design, development and construction of the Beamlines that transport light from the electron accelerator to the scientific sample. The Beamlines consist of optical elements and sample environments that employ sub-micron, multi-axis, precision motion systems operating in Ultra High Vacuum environments and often at cryogenic temperatures.}
         \resumeItem{Technologies}
          {ANSYS, MATLAB, SIMULINK, CREO, cryogenics, additive manufacturing, precision mechanisms, GD\&T, Digital signal processing, mechatronics}
      \resumeItemListEnd

    \resumeSubheading
      {Mapper Lithography}{Delft, NL}
      {Junior Mechanical Engineer: Wafer Loading Systems, Vacuum Support Systems}{Jan. 2016 - Dec. 2018}
      \resumeItemListStart
        \resumeItem{Description}
          {MAPPER Lithography is developing a ground-breaking maskless lithography infrastructure for the semiconductor industry. The tools utilize an innovative multiple e-beam technology with which next generation semiconductors can be manufactured in a more cost-effective fashion.}
        \resumeItem{Technologies}
          {SolidEdge, Solidworks, UHV systems, GD\&T, DFM, Pneumatics, Agile Scrum, Excel, MathCAD}
      \resumeItemListEnd

    \resumeSubheading
      {EPCM Consultants SA}{Centurion, RSA}
      {Vacation work: Engineering, Procurement and Construction Management}{Nov. 2014 - Jan. 2015}
      \resumeItemListStart
        \resumeItem{Description}
          {A specialist engineering, procurement and construction management company that focuses on oil and gas pipelines, tank farms and aviation fuel systems for various clients in Africa. The company also offers smart asset management software to ensure integrity during maintenance and operation of the clients assets.}
         \resumeItem{Technologies}
          {Solidworks, Excel, GIS}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------QUALIFICATIONS-----------------
\section{Qualifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MSc Computer Science (Robotics)} {University Of The Witwatersrand}
      {Graduation with distinction, Postgraduate Merit Award (2022, 2023)}{Jan. 2022 -- Dec. 2023}
        \resumeSubHeadingListStart
			\resumeSubItem{Dissertation}
      		{Real-time RoboCup Ball tracking by object detection using neural network aided Kalman filtering}
		\resumeSubHeadingListEnd
    \resumeSubheading
      {Chartered Engineer} {Institution of Mechanical Engineers}
      {}{Awarded Oct. 2021}
    \resumeSubheading
      {BEng Mechanical Engineering}{University Of Pretoria}
      {Graduation with distinction, Dean's list, Achievement award (2012, 2013, 2014, 2015)}{Jan. 2012 -- Dec. 2015}
    	\resumeSubHeadingListStart
			\resumeSubItem{Dissertation}
      		{Topology optimization of a compliant gripper}
		\resumeSubHeadingListEnd
     \resumeSubheading
      {National Senior Certificate}{St David’s Marist Inanda}
      {8 distinctions, Top Mathematics Student Award, Academic Honours Award}{Jan. 2007 -- Dec. 2011}
  \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------------
\section{Publications}
  \resumeSubHeadingListStart
    \resumeSubItem{A Vacuum Aspirated Cryo Cooling System}
      {Coauthor -- Proceedings MEDSI 2023, Beijing, China, 2023}
    \resumeSubItem{Innovative Delta Robot Sample Scanner}
      {Coauthor -- Journal of Physics: Conference Series, Volume 2380, 2022}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
