%-------------------------
% Resume in Latex
% Author: Patrick King
% Template by: Sourabh Bajaj
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks = true,
    urlcolor = {blue},
    linkbordercolor = {blue},
    pdfborderstyle = {/S/U/W 1},
}

\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}
}

\newcommand{\resumeSubtitle}[2]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Patrick King} & Mobile: +1-503-805-4667 \\
  \href{patrick@patrickcking.com}{patrick@patrickcking.com} & Location: Portland, OR\\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {New Relic}{Portland, OR}
    \resumeSubtitle
      {Senior Software Engineer - Database Engineering}{May 2018 - Present}
      \resumeItemListStart
        \resumeItem{Databases in Containers}
          {Built and maintained software written in Golang that allowed us to quickly deploy 2000+ databases in Docker containers across all of our environments.}
        \resumeItem{Bare-metal server Deployments}
          {Codified our bare-metal server deployments in Ignition and reduced deployment time by 90\%.}
        \resumeItem{Encryption at Rest}
          {Integrated dm-crypt into our database deployment pipeline so that all database volumes were automatically encrypted.}
        \resumeItem{FedRAMP Certification}
          {Worked with our Security team satisfy FedRAMP Moderate requirements for our database deployments.}
         \resumeItem{MySQL Sharding}
          {Deployed Vitess to transparently shard our largest MySQL database.}
        \resumeItem{Other Achievements}
          {
            \begin{itemize}[noitemsep]
            \item Deploy a fully automated database backup and restore pipeline with Jenkins.
            \item Introduced and productionized clustered Redis for single-source-of-truth data.
            \item Used the VividCortex API to create a whitelist and blacklist application to manage which databases we monitored.
            \item Automated alert creation using dimensions found in Telegraf data.
            \end{itemize}
          }
      \resumeItemListEnd
      \resumeSubtitle
      {Technical Product Manager - Database Engineering}{Nov 2018 - Present}
      \resumeItemListStart
         \resumeItem{Migration to the Cloud}
          {Engaged with management and architecture teams to plan out the Database Team's role in New Relic's cloud migration.}
        \resumeItem{Team Quarterly Planning}
          {Worked with stakeholders and multiple management levels to plan and prioritize the Database Team's quarterly schedule.}
      \resumeItemListEnd

    \vspace{15pt}
    \resumeSubheading
      {Yelp}{San Francisco, CA}
    \resumeSubtitle
      {Data Reliability Engineer}{May 2016 - December 2017}
      \resumeItemListStart
        \resumeItem{MySQL Database Server Auto Scaling}
          {Built software that intelligently scaled our MySQL clusters based on CPU usage and average query time leveraging in house tooling as well as custom automation written in Python.}
        \resumeItem{PostgreSQL Optimization}
          {Responsible for optimizing multiple PostgreSQL database clusters for better performance, which reduced the number AWS instances resulting in a substantial cost savings.}
        \resumeItem{Operational Maintainability}
          {Migrated all of the DRE team's SignalFX charts and detectors from manually created dashboards to use SignalForm to support our "Alerts as Code" initiative.}
        \resumeItem{MySQL Specific AMI}
          {Reduced production database deployment time by 75\% by rewriting the bootstrapping process using Packer to build custom baked MySQL images.}
        \resumeItem{Other Achievements}
          {
            \begin{itemize}[noitemsep]
            \item Upgraded MySQL across all environments to the most recent major version.
            \item Wrote a tool that would compare MySQL binary logs between two version of MySQL.
            \item Leveraged data contained in Splunk to write a predictive disk space alert for our MySQL servers.
            \item Deployed VividCortex as a database monitoring solution, and taught courses on how to use its data.
            \end{itemize}
          }
      \resumeItemListEnd

    \vspace{15pt}
    \resumeSubheading
      {Pandora Media, Inc}{Oakland, CA}
    \resumeSubtitle
      {Database Administrator}{May 2013 - April 2016}
      \resumeItemListStart
        \resumeItem{PostgreSQL Automated Backup Testing}
          {Created an automation pipeline in Python to backup our 200+ production PostgreSQL databases, restore them to verify backup was valid, and attach them to the appropriate replication stream to make sure we could use the backup in a DR scenario.}
        \resumeItem{Automatic Setup of PostgreSQL Replica Servers}
          {Implemented service discovery for database bootstrapping and replication, saving the DBA team hundreds of hours of manual configuration.}
        \resumeItem{PostgreSQL Performance Analysis Tooling}
          {Developed a pluggable framework to gather time-series metrics, and then used that to gather internal PostgreSQL metrics for performance analytics.}
        \resumeItem{Other Achievements}
          {
            \begin{itemize}[noitemsep]
            \item Major upgrade of PostgreSQL across our entire environment.
            \item Hadoop and Hive administration.
            \end{itemize}
          }
      \resumeItemListEnd

    \vspace{15pt}
    \resumeSubheading
      {Rentrak}{Portland, OR}
    \resumeSubtitle
      {Database Administrator}{August 2011 - May 2013}
        \begin{itemize}[noitemsep]
        \item Decreased PostgreSQL backup time by a factor of ten.
        \item Implemented read-only database clones by leveraging NetApp snapshots.
        \item Migration from physical PostgreSQL servers to HA VMware/NetApp environment.
        \item Developed and delivered internal auditing tools that decreased the DBA workload.
        \end{itemize}

    \vspace{15pt}
    \resumeSubheading
      {Elemental Technologies}{Portland, OR}
    \resumeSubtitle
      {Software Test Engineer (Contract)}{January 2011 - June 2011}
        \begin{itemize}[noitemsep]
        \item Worked on testing Elemental's two main products for compliance to many different video standards. Daily tasks included encoding and watching different video files, as well as watching live video. I was also responsible for the performance testing on Elemental's major releases.
         \end{itemize}

  \resumeSubHeadingListEnd


%-----------CONFERENCE TALKS-----------------
\section{Conference Presentations}
  \resumeSubHeadingListStart
    \resumeSubItem{App Sharded Redis w/Sentinel vs Redis Cluster - RedisConf19}
      {Presented with my coworker Cory Johannsen about our journey of scaling Redis and our use of many Redis sharding technologies.}
    \resumeSubItem{PostgreSQL to MySQL: A DBA Perspective - Percona Live 2017}
      {My retrospective after one year of transitioning from a PostgreSQL DBA to a MySQL DBA.}
    \resumeSubItem{Using pg\_repack to Bulk Delete Data - Postgres Vision 2016}
      {A 15 minute presentation about using  pg\_repack to bulk delete data from highly contested tables.}
  \resumeSubHeadingListEnd


%--------TECHNOLOGY SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Technologies}
      {PostgreSQL, MySQL, Redis, Vitess, Docker, Kubernetes, Puppet, AWS, Terraform, Ignition, Vault, New Relic, SignalFX, Splunk, VividCortex}
    \resumeSubItem{Languages}
      {Golang, Python, SQL, Bash}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
