%-------------------------
% Resume in Latex
% Author : Wilmer Gonzalez
% Based on: Sourabh Bajaj repo
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Page coloring, fonts, and logos
\usepackage{pagecolor}
\usepackage{lato}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{fontawesome}
% ---

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% ---

% Sections formatting
\titleformat{\section}{
  \vspace{1pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% ---

% Custom commands

\newcommand{\sepsection}{\vspace{25pt}}

\newcommand{\resumeItem}[1]{%2
  \item\small{
    %\textbf{#1}
    #1
    %{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{8pt}\item%-1
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \vspace{1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeTech}[2]{
 \underline{#1:} #2
}

% COLOR THEMES SELECTION

% For Light theme un-comment this and comment the Dark theme section below
\colorlet{textcolor}{black}
\colorlet{urlcolor}{blue}
\newcommand{\otherThemeRef}{\href{https://github.com/wilmeragsgh/resume/raw/master/wilmer_gonzalez_dark.pdf}{ Dark \color{urlcolor}{\faicon{lightbulb-o}}}}
\newcommand{\latestVersion}{\href{https://github.com/wilmeragsgh/resume/raw/master/wilmer_gonzalez_light.pdf}{Latest \color{urlcolor}{\faicon{refresh}}}}

\begin{document}
% ---

% For Dark theme un-comment this and comment the Light theme section above
% \colorlet{textcolor}{white!80!gray}
% \colorlet{backgroundcolor}{black!30!gray}
% \colorlet{urlcolor}{blue!25!white}
% \AtBeginDocument{\color{textcolor}}
% \newcommand{\otherThemeRef}{\href{https://github.com/wilmeragsgh/resume/raw/master/wilmer_gonzalez_light.pdf}{Light \color{urlcolor}{\faicon{lightbulb-o}}}}
% \newcommand{\latestVersion}{\href{https://github.com/wilmeragsgh/resume/raw/master/wilmer_gonzalez_dark.pdf}{Latest \color{urlcolor}{\faicon{refresh}}}}

% \begin{document}
% \pagecolor{backgroundcolor}
% ---

% HEADING
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Wilmer A. Gonzalez S.} \href{https:wilmerags.com}{\color{urlcolor} \faicon{link}}\\
  Machine learning engineer & \href{mailto:wilmeragsgm@gmail.com}{\color{urlcolor}{\faicon{envelope}} \color{textcolor} wilmeragsgm} \\
  \textsl{Caracas, Venezuela.} & \href{https://www.linkedin.com/in/wilmeragslin/}{ \color{urlcolor}{\faicon{linkedin}} \color{textcolor} wilmeragslin} \\
  \textsl{\small \latestVersion} /\textsl{\small \otherThemeRef} & \href{https://github.com/wilmeragsgh}{  \color{urlcolor}{\faicon{github}} \color{textcolor} wilmeragsgh}\\
\end{tabular*}
% ---

% EXPERIENCE
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Brightflow.AI}{(remote) Caracas, VE}
      {Machine learning engineer}{May 2023 - Present}
      \resumeItemListStart
      \resumeItem{Enable usage of industry data and models to enhance financial metrics for business owners.}
      \resumeItem{Grown and categorize 1.7M brands to be used by customers.}
      \resumeItemListEnd
      \resumeTech{Technologies}{AWS, Python, BERT, OpenAI ChatGPT, Athena.}\\
    %   \resumeTech{Theory}{Machine learning, AutoML, Feature engineering, Project management.}
    \sepsection

    \resumeSubheading
      {Sigma}{(remote) Caracas, VE}
      {Senior Machine learning engineer}{June - September, 2023}
      \resumeItemListStart
      \resumeItem{Develop misleading claims detection in advertising by using Google's LLM and prompt engineering.}
      \resumeItem{Integrate third-party ML services for feature detection and moderation on advertising creatives (image and text-based).}
      \resumeItem{Develop instruments for validation and comparison of third-party ML services.}
      \resumeItemListEnd
      \resumeTech{Technologies}{Large Language Models (LLM), Prompt Engineering, Vertex AI, Google Cloud Platform (GCP), Python, Natural Language Processing (NLP).}\\
    %   \resumeTech{Theory}{Machine learning, AutoML, Feature engineering, Project management.}
    \sepsection
  
    \resumeSubheading
      {CircleUp (Acquired by Brightflow.AI)}{(remote) Caracas, VE}
      {Machine learning engineer}{August 2021 - June 2023}
      \resumeItemListStart
      \resumeItem{Enable ML monitoring practices across 5 use-cases in the CPG industry.}
      \resumeItem{Enable semantic comparison of 1.7M brands and a hundred thousand text attributes.}
      \resumeItem{Improve and maintain classification pipelines of millions of observations with tens of GB-scale text data.}
      \resumeItemListEnd
      \resumeTech{Technologies}{AWS, GCP, Python, PySpark, Airflow, Vertex, BigQuery, Dataproc, Tensorflow, BERT.}\\
    %   \resumeTech{Theory}{Machine learning, AutoML, Feature engineering, Project management.}
    \sepsection

    \resumeSubheading
      {UNDP (UN)}{Caracas, VE}
      {Machine learning engineer}{August 2019 - August 2021}
      \resumeItemListStart
      \resumeItem{Provide summaries from opinions and trends by processing 1.1M tweets with Topic Modeling \newline and transformer based models.}
      \resumeItem{Detect key actors and information hubs by processing 150k user's data with Network analysis.}
      \resumeItem{Sped up the analytical workflow by 75\% by redesigning the sampling strategy for jobs.}
      \resumeItemListEnd
      \resumeTech{Technologies}{Python, R, Bash, Gephi, Power BI, REST API, Vue, Airflow, Kubernetes, Tensorflow, BERT, NLP, Data engineering, Data visualization, Workflow orchestration, Social networks analytics.}\\
    %   \resumeTech{Theory}{Topic modeling, Community detection, Network Analysis and NLP, Data visualization, Data engineering}
    
    \sepsection

    \resumeSubheading
      {Quash}{(remote) Caracas, VE}
      {Machine learning engineer}{March - July, 2021}
      \resumeItemListStart
      \resumeItem{Technical guide of the Data Science team.}
      \resumeItem{Improve the adaptability of the scoring API by creating 10+ features engineering stages.}
      \resumeItem{Deploy personalized ML models for credit scoring, processing 10k+ applications across 5+ countries.}
      \resumeItemListEnd
      \resumeTech{Technologies}{Python, R, AWS, Sagemaker, REST APIs.}\\
      
    \sepsection

    \newpage
    \resumeSubheading
      {Universidad Central de Venezuela}{Caracas, VE}
      {Adjunct professor (Advanced topics in AI)}{October 2018 - June 2021}
      \resumeItemListStart
      \resumeItem{Designed and organized course material and resources for topics described in \href{https://bit.ly/2VYchte}{\textsl{here}}.}
      \resumeItem{Lectured material for students and grade their assignments.}
      \resumeItem{Tutored thesis work on AI related to computer vision \newline \textsl{(Awarded with country-wise recognition for thesis work between 6 final candidates)}.}
      \resumeItemListEnd
    \resumeSubSubheading
      {Teaching assistant (Introduction to Data Science, Data Mining)}{April 2015 - February 2018}
     \resumeItemListStart
      \resumeItem{Designed and organized practical course material and resources for topics described in \href{https://bit.ly/2VYchte}{\textsl{here}}.}
      \resumeItem{Lectured practical material for students and grade their assignments.}
      \resumeItemListEnd
      \resumeTech{Technologies}{Python, Latex, R, Weka, Colab, Jupyter and swirl.}\\
    %   \resumeTech{Theory}{Artificial intelligence, Data science and Data mining.}

    \resumeSubheading
      {Omdena}{(remote) Caracas, VE}
      {Lead machine learning engineer}{Jan - Apr, 2021}
      \resumeItemListStart
      \resumeItem{Helped create a trust score for news articles by implementing a claim detection model.}
      \resumeItem{Improved usability of the product by creating a chrome extension connected to resultant models.}
      \resumeItem{Contributed to open-source projects related to NLP and Deep Learning models.}
      \resumeItemListEnd
      \resumeTech{Technologies}{Python, Keras, Tensorflow, Falcon, REST APIs, Javascript.}\\
    %   \resumeTech{Theory}{NLP, Deep Learning, Web development.}

\sepsection
    \resumeSubheading
      {Oliver Wyman}{(remote) Caracas, VE}
      {Data engineer}{July - November, 2020}
      \resumeItemListStart
      \resumeItem{Enabled data pipelines processing by provisioning and configuring Airflow.}
      \resumeItem{Created DAGs for 30+ stored procedures from SQL Server scripts.}
      \resumeItem{Created DAGs for importing tabular data (1M+ records) to SQL Server.}
      \resumeItemListEnd
      \resumeTech{Technologies}{Python, Airflow, SQL Server, Jenkins, Rancher, Docker, Kubernetes.}\\
    %   \resumeTech{Theory}{Data pipelines orchestration, ETL, Provisioning.}

    \sepsection

    \resumeSubheading
      {Quash}{(remote) Caracas, VE}
      {Machine learning engineer}{February 2019 - March 2020}
      \resumeItemListStart
      \resumeItem{Developed a customer facing API for using our internal credit scoring model.}
      \resumeItem{Increased approval rate by 15\% of customers while keeping the same risk by optimizing state-of-the-art ML models.}
      \resumeItemListEnd
      \resumeTech{Technologies}{Python, R, S3 and Docker.}\\
    %   \resumeTech{Theory}{Credit scoring and Hyper-parameter optimization.}

    \sepsection

    \resumeSubheading
      {Advoqt}{(remote) Caracas, VE}
      {Machine learning engineer}{February - August, 2019}
      \resumeItemListStart
      \resumeItem{Increased security by implementing a Deep Learning model for classifying malicious urls with high accuracy.}
      \resumeItemListEnd
      \resumeTech{Technologies}{Python, Tensorflow, Elasticsearch and Spark.}\\
    %   \resumeTech{Theory}{Deep learning and Text classification.}

    \sepsection
    \newpage
    \resumeSubheading
      {Fetcher}{Caracas, VE}
      {Data scientist}{June 2018 - February 2019}
      \resumeItemListStart
      \resumeItem{Decreased overload of sourcing teams by 10\% by creating an automated allocation algorithm using Linear programming and Constraint Satisfaction techniques.}
      \resumeItem{Estimated demand of required candidates for sourcing using daily output data.}
      \resumeItemListEnd
      \resumeTech{Technologies}{R, Shiny, Latex, SQL and Metabase.}\\
    %   \resumeTech{Theory}{Linear programming and Constraint Satisfaction problems.}

%\newpage

    \sepsection
    
    \resumeSubheading
      {Predictvia}{Caracas, VE}
      {Machine learning engineer}{February 2016 - January 2017}
     \resumeItemListStart
     \resumeItem{Performed social network analysis, exploratory data analysis, supervised and unsupervised learning.}
     \resumeItem{Built and implemented classification models, perform feature engineering, and calibrated existing models.}
     \resumeItemListEnd
     \resumeTech{Technologies}{Python, bash.}\\
    %  \resumeTech{Theory}{Social network analysis, Attribution models and  Recommendation systems.}
    \resumeSubHeadingListEnd
% ---
\newpage
% PROGRAMMING SKILLS
\section{Technical skills}
  \resumeSubHeadingListStart
  
  \resumeSubItem{\textbf{Programming languages:} Python, R, Bash, Julia.}
  
  \resumeSubItem{\textbf{Cloud services:} AWS (Lambda, S3, Sagemaker), GCP (AI Platform), Azure (Blob storage).}
  
  \resumeSubItem{\textbf{Deep learning frameworks:} Keras, Tensorflow.}
  
  \resumeSubItem{\textbf{Others:} xgboost, scikit, pandas, falcon, flask, fastapi, Docker, Kubernetes, Jenkins, Terraform}

  \resumeSubItem{\textbf{Currently learning:} Transformers models, Vue, Nodejs.}
  
  \resumeSubHeadingListEnd

% EDUCATION
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universidad Central de Venezuela}{Caracas, Venezuela}
      {B.Sc in Computer Science}{Sept. 2012 -- Jun. 2018}
      \resumeItemListStart
      \resumeItem{Took elective courses on: Introduction to data science, Advanced topics in data science, Artificial Intelligence, Data mining, Text mining, NoSQL databases, Digital image processing.}
      \resumeItem{(Thesis title) AdaBnn: Binarized Neural Networks trained with adaptive structural learning.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
% ---
\vspace{1em}
% \hfill \textsl{ Click on items for details. \color{urlcolor}{\faicon{link}}}

% CERTIFICATIONS
\section{Certifications \color{urlcolor}{(with links)}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {@ Udacity/Coursera}{MOOC}
      {\href{https://www.coursera.org/account/accomplishments/specialization/58JWPP7YSWY3}{Machine Learning Engineering for Production (MLOps) Specialization}}{Issued July 2022}
    
    % \resumeSubheading
    %   {Coursera}{MOOC}
    \resumeSubSubheading
      {\href{https://graduation.udacity.com/confirm/AWGF3KVQ}{Machine learning engineer nanodegree}}{Issued March 2021}
    
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/specialization/certificate/WYGXVXA327K9}{Deep learning specialization}}{Issued January 2021}
    
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/verify/HEURLGHTW46G}{Sequence models}}{Issued January 2021}
      
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/verify/U59ZPPWP5NRN}{Convolutional neural networks}}{Issued September 2020}
    
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/verify/BHN34W5WKBUT}{Structuring machine learning projects}}{Issued May 2020} 
   
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/records/J76SQGG4PVYL}{Improving deep neural networks: Hyperparameter tuning, regularization and optimization}}{Issued May 2020}
     
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/verify/MBWJ69CVLQAZ}{Neural networks and deep learning}}{Issued May 2020}
      
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/certificate/MZ7TC7ADV7YY}{R Programming}}{Issued September 2016}
      
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/certificate/36JC577GBFYD}{Text mining and analytics}}{Issued August 2016}
     
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/certificate/MDWATFKLPH9Z}{Text retrieval and search engines}}{Issued June 2016}
     
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/certificate/TM7T8CJXNV6R}{The data scientist's toolbox}}{Issued June 2016}
     
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/certificate/WYGG7TDFPB3F}{Data visualization}}{Issued March 2016}
  \resumeSubHeadingListEnd
% ---

%\newpage
\vspace{1em}
% PROJECTS
\section{Personal Projects \color{urlcolor}{(with links)}}

  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/wilmeragsgh/philia}{Philia: A Slack bot for empathy assessment in co-workers communications.}}
    
    \resumeSubItem{\href{https://github.com/wilmeragsgh/adabnn}{AdaBnn: Binarized Neural Networks trained with adaptive structural learning.}}

    \resumeSubItem{\href{https://github.com/wilmeragsgh/WarmChat}{WarmChat: Chat room web app that classifies insults messages by using several classifiers.}}
    
    \resumeSubItem{\href{https://github.com/wilmeragsgh/term_freq_linkedin}{Small tool for generating frequent words analysis on the position names of LinkedIn Connections.}}
    
    \resumeSubItem{\href{https://github.com/wilmeragsgh/shinycker}{Template for dockerized shiny (R) application deployment.}}
    
    \resumeSubItem{\href{https://github.com/wilmeragsgh/resume}{Latex template for CVs with dark theme, with CV guidelines from google.}}
    
  \resumeSubHeadingListEnd
% ---

\vspace{1em}

% PERSONAL PUBLICATIONS
\section{Personal publications \color{urlcolor}{(with links)}}

  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://omdena.com/blog/fighting-misinformation/}{Mahfuzur Rahman, Ann Chia, Wilmer Gonzalez. Fighting Misinformation and Fake News using NLP
. 09/2021}}

    \resumeSubItem{\href{http://scivisionpub.com/pdfs/diodes-laser-in-office-endoscopic-surgery-center-for-nasal-obstruction-and-snoring-558.pdf}{Sajidxa Mariño, Jesus Lares, Wilmer Gonzalez. Diode’s Laser in Office Endoscopic Surgery Center for Nasal Obstruction
and Snoring. J Med - Clin Res \& Rev. 2018; 2(6): 1-3.}}

    \resumeSubItem{\href{https://www.slideshare.net/WilmerGonzalez7/twitter-a-data-source-for-the-academy}{Twitter, A data source for the academy (spanish).}}
    
    \resumeSubItem{\href{https://www.slideshare.net/WilmerGonzalez7/github-social-coding-the-social-network-for-programmers}{GitHub \& Social Coding. Social network for programmers (spanish).}}
    
    \resumeSubItem{\href{https://www.slideshare.net/WilmerGonzalez7/reproducible-research-a-case-of-study-on-allocation-of-university-places}{Reproducible Research. Case of study: allocation of university places in UCV by OPSU (spanish).}}
    
  \resumeSubHeadingListEnd
% ---

%\hfill \textsl{ Not clickable anymore.}


% ---
\end{document}
