%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProject}[1]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeResearch}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} {\small #4 \vspace{-2pt}} & \textit{\small #5} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeTalk}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeLeadership}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://changh95.github.io}{\Large Hyunggi Chang}} & Email : \href{mailto:hyunggi.chang95@gmail.com}{hyunggi.chang95@gmail.com}\\
  \href{http://changh95.github.io}{http://changh95.github.io} & Mobile : (+82) 010-2885-4493 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Imperial College London}{London, UK}
      {M.Res. in Medical Robotics and Image-Guided Intervention;  \textbf{Merit}}{Oct. 2017 -- Sept. 2018}
    \resumeSubheading
      {University of Warwick}{Coventry, UK}
      {B.Eng. in Manufacturing and Mechanical Engineering; \textbf{GPA (4.34/4,50)}}{Oct. 2014 -- Jun. 2017}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Research Experiences}
  \resumeSubHeadingListStart

    \resumeResearch
      {Cavendish Laboratory, University of Cambridge}{Cambridgeshire, UK}
      {Visiting Researcher,}{Advisor: Dr. Sarah Bohndiek}{Jan. 2019 - Mar. 2019}
      \resumeItemListStart
        \resumeItem {3.5D hyperspectral point cloud generation, using Structure from Motion (SfM) and spectral-spatio-matching.}
        \resumeItem {Wide-field multi-fibre endoscopic imaging device simulation.}
      \resumeItemListEnd
      
    \resumeResearch
      {Surgical Imaging and Biophotonics Laboratory, Imperial College London}{London, UK}
      {M.Res Student Researcher,}{Advisor: Prof. Daniel Elson}{Jan. 2018 - Sept. 2018}
      \resumeItemListStart
        \resumeItem {Real-time vision-based surgical tool tracking and augmented reality visualisation.}
        \resumeItem {Real-time biomedical spectroscopic data classification using machine learning.}
      \resumeItemListEnd
      
      \resumeResearch
      {HARMS Lab, Imperial College London}{London, UK}
      {M.Res Student Researcher,}{Advisor: Dr. George Mynolas}{Oct. 2017 - Dec. 2017}
      \resumeItemListStart
        \resumeItem {Hand motion transfer to robotic movements in surgical scenarios.}
        \resumeItem {Design improvements of an endoscopic robot.}
      \resumeItemListEnd
      
    \resumeResearch
      {Trace Metals in Medicine Laboratory, University of Warwick}{Coventry, UK}
      {B.Eng Student Researcher,}{Advisor: Dr. Joanna Collingwood}{Oct. 2016 - Jun. 2017}
      \resumeItemListStart
        \resumeItem {Design of an educational MRI phantom for deliberate artifact generation.}
      \resumeItemListEnd
     
     \resumeResearch
      {International Institute for Product and Service Innovation, WMG}{Coventry, UK}
      {B.Eng Student Researcher,}{Advisor: Mr. Graeme Knowles}{Oct. 2016 - Jun. 2017}
      \resumeItemListStart
        \resumeItem {Qualitative study in quality engineering techniques.}
      \resumeItemListEnd
     
      
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Work Experiences}
  \resumeSubHeadingListStart

    \resumeSubheading
      {VIRNECT}{Seoul, South Korea}
      {Computer Vision Research Engineer}{Apr. 2019 - Present}
      \resumeItemListStart
        \resumeItem
          {Research and develop geometric vision algorithms for augmented reality applications.}
      \resumeItemListEnd

    \resumeSubheading
      {McKinsey \& Company}{New York, USA}
      {Student Analyst}{Oct 2017 - Dec 2017}
      \resumeItemListStart
        \resumeItem
        {Market analysis and forecast of commercial robot and artificial intelligence technology.}    
        \resumeItem
        {Taught McKinsey business consultants on robotics industry.}
      \resumeItemListEnd

    \resumeSubheading
      {CACTUS Communications}{London, UK}
      {Freelance Translator}{Oct. 2016 - Jun. 2018}
      \resumeItemListStart
        \resumeItem
          {Translated MS/PhD thesis and papers from Korean to English and vice-versa on various engineering fields.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Skills-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{Languages :}}
      {Korean (Native), English (Bilingual)}
    \resumeSubItem{\textbf{Programming :}}
      {C, C++11/14, MATLAB, Python}
    \resumeSubItem{\textbf{Computer Vision :}}
      {OpenCV, Eigen, Ceres-solver, FFmpeg, Dlib, PyTorch, OpenVINO,  MeshLab }
    \resumeSubItem{\textbf{Camera :}}
      {Intel RealSense, MS Kinect, Stereolabs ZED, FLIR Spinnaker, Optitrack Motive}
    \resumeSubItem{\textbf{Prototype :}}
      {SolidWorks, AutoCAD, AlphaCAM, 3D Printer, Laser cutter, Core workshop machines}
    \resumeSubItem{\textbf{Collaborative Development :}}
      {Git, GTest, Clang-format, Doxygen, JIRA, Slack, TeamCity}
    \resumeSubItem{\textbf{Other :}}
      {Rpi, Arduino, Nvidia Jetson, ROS, AirSim, ABB Robot Studio, CMake, LaTeX}
    \resumeSubItem{\textbf{Next 6 months :}}
      {CUDA, TensorRT, ONNX, PCL}
  \resumeSubHeadingListEnd

%-----------Projects-----------------

\section{Projects}
  \resumeSubHeadingListStart
    \resumeProject
      {SLAM to Replace Light Probe}
      \resumeItemListStart
        \resumeItem {Semi-dense SLAM that is aware of light-sources to create an environmental cube map for ray-tracing.}
      \resumeItemListEnd
    \resumeProject
      {VIRNECT AR SDK}
      \resumeItemListStart
        \resumeItem {Generation of test data and ground-truth data, using AirSim and Optitrack Motion Capture.}
        \resumeItem {Evaluation and validation of image tracking and SLAM algorithms with automatic report generation.}
        \resumeItem {GTest for software quality assurance of vision algorithms.}
      \resumeItemListEnd
    \resumeProject
      {Real-Time Welding Guidance using Augmented Reality}
      \resumeItemListStart
        \resumeItem {Tracking of welding torch and HMD using fiducial markers and IMU under extreme light condition.}
      \resumeItemListEnd
    \resumeProject
      {Marker-based Tool Tracker on Tabletop Scenario and Novel Multi-Camera Calibration Method}
      \resumeItemListStart
        \resumeItem {Multi-view tool tracking using Perspective-n-Points (PnP) Algorithm with optimisation for minimal reprojection error.}
        \resumeItem {Auto-calibration of camera extrinsics and the geometric relationship of marker-to-tooltip.}
      \resumeItemListEnd
    \resumeProject
      {Building IR Motion Capture System with IMU, F/T, Video Genlock}
      \resumeItemListStart
        \resumeItem {System setup of motion/dynamics capture system using Optitrack IR cameras, RGB cameras, IMU, and force/torque sensors on perfect time sync.}
      \resumeItemListEnd
    \resumeProject
      {Affordable Hyperspectral Imaging System}
      \resumeItemListStart
        \resumeItem {System setup of an affordable hyperspectral imaging rig, using light-sources of various spectral bands.}
      \resumeItemListEnd
    \resumeProject
      {Omni-directional RGB-D Camera}
      \resumeItemListStart
        \resumeItem {Real-time omni-directional RGB-D imaging, using multiple RGB-D Cameras.}
      \resumeItemListEnd
    \resumeProject
      {Mobile Rover for Environment Mapping and Survivor Detection in Disaster Scenarios}
      \resumeItemListStart
        \resumeItem {Voice-controllable rover, using RGB-D SLAM, object detection, and collision-avoidance.}
        \resumeItem {Award winning project at MODU Embedded AI Hackathon.}
      \resumeItemListEnd
    \resumeProject
      {Structure from Motion with Dynamic Objects}
      \resumeItemListStart
        \resumeItem {Attempt to extract static map from dynamic scene, using only epipolar constraints.}
      \resumeItemListEnd
    \resumeProject
      {Snapchat-like Face Filters}
      \resumeItemListStart
        \resumeItem {Spot-removal filter, AR Kawaii-filter, Emotion masks, and Panda-face filter, using OpenCV and Dlib.}
      \resumeItemListEnd
    \resumeProject
      {Make Surgical Scenes Less Disturbing}
      \resumeItemListStart
        \resumeItem {Reduced visual discomfort in surgical scenes via neural-style algorithm and frame buffer.}
      \resumeItemListEnd
    \resumeProject
      {Surgical Cobot Control with Gaze Control and QR Code Commands}
      \resumeItemListStart
        \resumeItem {A concept code to use cobots in surgical theatre to pick up and pass tools to surgeons}
      \resumeItemListEnd
    \resumeProject
      {Depth Mapping and Visualisation using Multiple Webcams}
      \resumeItemListStart
        \resumeItem {Real-time depth map generation using affordable webcams.}
      \resumeItemListEnd
    \resumeProject
      {A Real-Time Intraoperative Data Mapping Device for Probe-Based Measurements}
      \resumeItemListStart
        \resumeItem {Customised optical biopsy system, using diffuse reflectance spectroscopy.}
        \resumeItem {Multi-camera configuration for vision-based surgical instrument tracking.}
        \resumeItem {Design ergonomic control and visualisation hardware and system.}
      \resumeItemListEnd
    \resumeProject
      {Intraoperative Tissue Classification using Hyperspectral Sensing}
      \resumeItemListStart
        \resumeItem {Cancer identification from optical spectroscopic data, using machine learning.}
      \resumeItemListEnd
    \resumeProject
      {Vision-Based Endoscopic Navigation Using SLAM}
      \resumeItemListStart
        \resumeItem {Monocular visual SLAM on a rigid colon phantom.}
      \resumeItemListEnd
    \resumeProject
      {Motion Capture for Optimisation of Endoscopic Robot for Bi-Manual Suturing}
      \resumeItemListStart
        \resumeItem {Hand motion transfer from a surgeon to a surgical robot, using Optitrack and ATI F/T.}
        \resumeItem {Exploit and optimise the robot's mechanical configuration, based on required motion trends}
      \resumeItemListEnd
    \resumeProject
      {Robotic Path Planning for Beating Heart Surgery}
      \resumeItemListStart
        \resumeItem {MATLAB simulation for inverse kinematics of a PUMA robot on dynamic trajectory.}
      \resumeItemListEnd
    \resumeProject
      {Development of modular training phantom for MRI radiologists}
      \resumeItemListStart
        \resumeItem {Product development study for maximum customer satisfaction.}
        \resumeItem {An educational MRI phantom for deliberate image artifact generation}
      \resumeItemListEnd
    \resumeProject
      {Analysis of Industry 4.0 Manufacturing System Architecture on Quality Perspective}
      \resumeItemListStart
        \resumeItem {Literature review of technological advances on Industry 4.0.}
      \resumeItemListEnd
    \resumeProject
      {Text Writing Robot}
      \resumeItemListStart
        \resumeItem {ABB robot programming to convert text into physical writing.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------Patents-----------------

\section{Patents}
  \resumeSubHeadingListStart
    \resumeProject{Calibration Mechanism and Method for Posture Estimation of Augmented Reality Guide Tool}
    \resumeItemListStart
        \resumeItem{[PENDING] \textit{T.J.Ha, \textbf{H.G.Chang}, S.H.Kim} - Ref Num: TP191060}
    \resumeItemListEnd
    \resumeProject{Method and System for Posture Estimation about Object Tracking Taken by Camera}
    \resumeItemListStart
        \resumeItem{[PENDING] \textit{T.J.Ha, \textbf{H.G.Chang}, S.H.Kim, N.Y.Park} - Ref Num: TP191091}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------Leadership-----------------

\section{Leadership}
  \resumeSubHeadingListStart
    \resumeLeadership{\textbf{Community Leader} - Kakao Community ``We will be SLAM Masters"}{\textbf{2019}}
    \resumeLeadership{\textbf{Community Admin} - Facebook Community "AI Robotics KR"}{\textbf{2019}}
    \resumeLeadership{\textbf{Lead Student Ambassador} - Hamlyn Robotic \& AI Summer School}{\textbf{2018}}
    \resumeLeadership{\textbf{Journal Club Lead} - Imperial College London}{\textbf{2018}}
    \resumeLeadership{\textbf{Lead Student Researcher} - McKinsey \& Company}{\textbf{2017}}
    \resumeLeadership{\textbf{Course Representative} - Imperial College London}{\textbf{2017}}
    \resumeLeadership{\textbf{Course Representative} - University of Warwick}{\textbf{2016}}
  \resumeSubHeadingListEnd

%-----------Teaching-----------------
\section{Teaching}
    \resumeSubHeadingListStart
        \resumeSubheading{Fundamentals of Simultaneous Localisation and Mapping - ORB-SLAM}{Seoul, South Korea}
        {'We will be SLAM masters' study group}{Nov. 2019 -- PRESENT}
            \resumeItemListStart
                \resumeItem{Organised and led 2-months study on Modern C++ and fundamentals of SLAM.}
                \resumeItem{Leading 2-months course on in-depth review of ORB-SLAM and its source code.}
            \resumeItemListEnd    
        \resumeSubheading{Medical Imaging and Image-Guided Intervention}{Seoul, South Korea}
        {MODU Labs - Flipped Learning Scheme}{Oct.2019 -- Dec.2019}
            \resumeItemListStart
                \resumeItem{Taught on 11-weeks course on fundamentals of medical imaging and image-guided intervention.}
                \resumeItem{X-ray, CT, Ultrasound, Nuclear Medicine, MRI, Microscopy, Fluorescence Imaging, Image-Guided Intervention.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Talks-----------------
\section{Talks}
    \resumeSubHeadingListStart
        \resumeTalk{MODUCON 2019}{2019}
            \resumeItemListStart
                \resumeItem{Design considerations for robust computer vision systems}
                \resumeItem{Development strategies for Deep Learning}
            \resumeItemListEnd
        \resumeTalk{AI Robotics KR - The First}{2019}
            \resumeItemListStart
                \resumeItem{Camera hardware choices for robust computer vision systems}
            \resumeItemListEnd
        \resumeTalk{PyCon APAC 2019}{2019}
            \resumeItemListStart
                \resumeItem{Lightning Talk - Robot development with Python}
            \resumeItemListEnd
        \resumeTalk{NVIDIA Jetson Meetup}{2019}
            \resumeItemListStart
                \resumeItem{NVIDIA Jetson Nano for intelligent robot development}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
